%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV LaTeX Template Version 2.0 (8/5/13)
% This template has been downloaded from: http://www.LaTeXTemplates.com
% Important note: This template requires the resume.cls file to be in
% the same directory as the .tex file. The resume.cls file provides
% the resume style used for structuring the document.

% PACKAGES AND DOCUMENT CONFIGURATIONS -------------------------------
\documentclass{CV} % Use the custom resume.cls style
\usepackage[left=0.75in,top=1in,right=0.75in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{etaremune}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
% \usepackage{garamondx}
\usepackage{enumitem}
\hypersetup{colorlinks=true, urlcolor=blue}
\usepackage{parskip}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\renewcommand\thesubsection{}
\renewcommand\labelitemi{$-$}
\titlespacing*{\subsection}{0pt}{1ex}{0.2ex}

% HEADER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Rajat Verma}
% \company{Lyles School of Civil Engineering}
\address{Purdue University, West Lafayette IN 47907} % secondary address
\address{+1(517)481-0901 \\ \href{mailto:verma99@purdue.edu}{verma99@purdue.edu}} % phone number and email
\address{Lyles School of Civil Engineering} % primary address
% \setmainfont[Ligatures=TeX]{Lora-Regular}

\begin{document}

% RESEARCH INTERESTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{rSection}{Research Interests}
%     % very vague - be specific
%     Transportation equity, accessibility, urban planning, travel behavior, human mobility.
% \end{rSection}

% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Education}
    % Purdue
    {\bf Purdue University} \hfill {\em West Lafayette, IN}
    \\ Ph.D., Civil Engineering. Current GPA: 4.0. \hfill {8/2019 – 8/2024 (expecting)}
    \\ Advisor: \href{http://www.satishukkusuri.com/}{Dr. Satish V. Ukkusuri}
    \\ Dissertation: \emph{Advancing the quantitative assessment of transportation equity for planning}. \\
    % Michigan State
    \\ {\bf Michigan State University} \hfill {\em East Lansing, MI} 
    \\ Master of Science, Civil Engineering. GPA: 4.0 \hfill {8/2017 – 5/2019}
    \\ Advisor: \href{https://www.egr.msu.edu/people/profile/gatestim}{Dr. Timothy J. Gates}
    \\ Thesis: \emph{Evaluation of a rear-end collision avoidance system on winter maintenance trucks}. \\
    % IIT Roorkee
    \\ {\bf Indian Institute of Technology Roorkee} \hfill {\em Roorkee, India}
    \\ Bachelor of Technology, Civil Engineering. GPA: 8.64/10 \hfill {7/2013 – 5/2017}
    \\ Academic advisor: \href{https://civil.iitr.ac.in/CE?Uid=indrafce}{Dr. Indrajit Ghosh}
    \\ Major project: \emph{Design of sustainable drainage and rainwater harvesting for IIT Roorkee campus}.
\end{rSection}

% RESEARCH EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Work Experience}
    {\bf Teaching Assistant} \hfill {8/2023 – 12/2023}
    \\ Purdue University \hfill {\em West Lafayette, IN}
    \begin{itemize}[noitemsep]
        \item Course {\em CE 597: Data Science for Smart Cities}, instructed by Dr. Satish Ukkusuri
        \item Development and instruction of 6 introductory tutorial sessions for using Python for data analytics in Jupyter Lab in addition to other duties (office hours, grading, etc.).
    \end{itemize}
    % Purdue RA
    {\bf Graduate Research Assistant} \hfill {8/2019 – Present}
    \\ Purdue University \hfill {\em West Lafayette, IN}
    \begin{itemize}[noitemsep]
        \item Worked on a collection of projects to assess human mobility patterns at scale and their relation with inequitable distribution of accessibility to jobs, transit, and places of interest as well as environmental inequity. Projects sponsored by the National Science Foundation and Indiana Department of Transportation (DOT).
        \item Major outcomes/contributions include \href{https://umnilab.github.io/HSEES_doc/}{A-RESCUE 3.0}, a hurricane evacuation micro traffic simulator, \href{https://github.com/rvanxer/mk}{mobilkit}, a Spark-based Python toolkit for processing high-volume passively collected smartphone GPS data, and \href{https://github.com/rvanxer/spr_4711}{Spatial Accessibility of America}, a repository of spatial accessibility metrics developed for the 50 largest urban areas of the U.S.
    \end{itemize}
    % MSU RA
    {\bf Graduate Research Assistant} \hfill {8/2017 – 7/2019}
    \\ Michigan State University \hfill {\em East Lansing, MI}
    \begin{itemize}[noitemsep]
        \item Assessed the performance and effectiveness of a pilot rear-facing collision avoidance system on snowplows. Project sponsored by the Michigan DOT.
        \item Analyzed the effects of the 2017 speed limit change in Michigan on operating speeds based on three data sources.
        \item Developed OMR recognition system to automate processing of the annual state-wise safety belt survey data.
    \end{itemize}
    % Research intern
    {\bf Research Intern} \hfill {5/2016 – 6/2016}
    \\ Indian Institute of Science \hfill {\em Bengaluru, India}
    \\ Supervisor: \href{http://civil.iisc.ernet.in/~ashishv/}{Dr. Ashish Verma}
    \begin{itemize}[noitemsep]
        \item Worked on the project ``Spatial Analysis of Pedestrian Crowds” of the main project ``\textit{\href{http://www.the-kumbh-mela-experiment.com/}{The Kumbh Mela Experiment}: Measuring and Understanding the Dynamics of Mankind’s Largest Crowd}", Ujjain, India.
        \item Studied pedestrian traffic flow theory and the social force method to study the basic forms of interaction among pedestrian groups.
    \end{itemize}
\end{rSection}

% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Technical Strengths}
    \begin{tabbing}
    \textbf{Languages} \hspace*{0.5cm} \= Python$^*$, R$^*$, SQL$^*$, Java, MATLAB, Julia, HTML/CSS/JS, Bash$^*$.
    \\ \textbf{Frameworks} \> Pyspark$^*$, Pytorch, Tensorflow, Dash/Plotly$^*$, Jupyter$^*$, LaTeX$^*$, jQuery.
    \\ \textbf{Analytics} \> QGIS$^*$, ArcGIS$^*$, Tableau$^*$, SPSS$^*$, Excel$^*$, Gephi, AutoCAD.
    \\ \textbf{Simulation} \> PTV VISSIM.
    \\ \textbf{Creative} \> Figma$^*$, Photoshop$^*$, Illustrator$^*$, Canva$^*$.
    % \\ Languages \> English*, Hindi* (native), Spanish (basic).
    \end{tabbing}
    * Proficient.
\end{rSection}

% PUBLICATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Publications}
    % ----------------------------
    % Journal papers
    % ----------------------------
    \subsection*{Articles in Peer Reviewed Journals and Conferences}
    \begin{etaremune}
        \item Lei, Z., \underline{Verma, R.}, Siebeneck, L. \& Ukkusuri, S.V. Modeling hurricane evacuation/return under compounding risks – Evidence from Hurricane Ida. Under review in \textit{Transportation Research Part D: Transport and Environment} (2024).

        \item \underline{Verma, R.} \& Ukkusuri, S.V. What determines travel time and distance decay in spatial interaction and accessibility? Under review in \textit{Journal of Transport Geography} (2024).

        \item Siebeneck, L., Lei, Z., Sharma, P., \underline{Verma, R.}, Osazuwa-Peters, P. \& Ukkusuri, S.V. Household evacuation decision-making during simultaneous disasters: Hurricane Ida and the COVID-19 pandemic. Under review in \textit{International Journal of Disaster Risk Reduction} (2024).

        \item \underline{Verma, R.}, Mittal, S., Lei, Z., Chen, X. \& Ukkusuri, S.V. Comparison of home detection algorithms using smartphone GPS data.
        \textit{EPJ Data Science}, 13(6) (2024). doi: \href{https://doi.org/10.1140/epjds/s13688-023-00447-w}{10.1140/epjds/s13688-023-00447-w}
        
        \item \underline{Verma, R.} \& Ukkusuri, S. V. Crosswalk detection from satellite imagery for pedestrian network completion. \textit{Transportation Research Record}, 0(0) (2023). doi: \href{https://doi.org/10.1177/03611981231210545}{10.1177/03611981231210545}.
        \\ \textbf{Special coverage in a news article in The Washington Post} (\href{https://www.washingtonpost.com/transportation/2023/02/25/sidewalks-crosswalks-study/}{link}).
        
        \item \underline{Verma, R.} \& Ukkusuri, S. V. A link criticality approach for pedestrian network design to promote walking. \textit{npj Urban Sustainability}, 3(48) (2023). doi: \href{https://doi.org/10.1038/s42949-023-00114-z}{10.1038/s42949-023-00114-z}
        
        \item \underline{Verma, R.}, Shen, J., Benedict, B. C., Murray-Tuite, P., Lee, S. \& Ukkusuri, S. V. Progression of hurricane evacuation-related dynamic decision-making with information processing.\textit{Transportation Research Part D: Transport and Environment}, 108, 103323 (2021).\\doi: \href{https://doi.org/10.1016/j.trd.2022.103323}{10.1016/j.trd.2022.103323}
        
        \item \underline{Verma, R.}, Yabe, T. \& Ukkusuri, S.V. Spatiotemporal contact density explains the disparity of COVID-19 spread in urban neighborhoods. \textit{Scientific Reports}, 11(10952) (2021).
        \\ doi: \href{https://www.nature.com/articles/s41598-021-90483-1}{10.1038/s41598-021-90483-1}
        
        
        \item \underline{Verma, R.}, Lei, Z., Xue, J., Shen, J., Gehlot, H., Ukkusuri, S.V. \& Murray-Tuite, P. How information heterogeneity influences traffic congestion during hurricane evacuation.
        \\ \textit{2021 IEEE International Intelligent Transportation Systems Conference (ITSC)}, 1833-1838 (2021). doi: \href{https://ieeexplore.ieee.org/document/9564797}{10.1109/ITSC48978.2021.9564797}

        \item Saedi, R., \underline{Verma, R.}, Zockaei, A., Ghamami, M. \& Gates, T.J. Comparison of support vector and non-linear regression models for estimating large-scale vehicular emissions, incorporating network-wide fundamental diagram for heterogeneous vehicles. \textit{Transportation Research Record}, 2674(5), 70–84 (2020). doi: \href{https://journals.sagepub.com/doi/abs/10.1177/0361198120914304}{10.1177/0361198120914304}
        
        \item \underline{Verma, R.}, Saedi, R., Zockaie, A. \& Gates, T.J. Behavioral analysis of drivers following winter maintenance trucks enabled with collision avoidance system. \textit{Transportation Research Record}, 2673(10), 394-404 (2019). doi: \href{https://journals.sagepub.com/doi/abs/10.1177/0361198119850131}{10.1177/0361198119850131}
        
        \item Saedi, R., \underline{Verma, R.}, Zockaei, A., Ghamami, M. \& Gates, T.J. A framework for incorporating the network fundamental diagram into large-scale emission estimation. \textit{Journal of Transport \& Health} 9, S54-S55 (2018). doi: \href{https://www.sciencedirect.com/science/article/abs/pii/S2214140518302263}{10.1016/j.jth.2018.05.041}
    \end{etaremune}
    
    % -------------------------------
    % Papers in progress
    % -------------------------------
    \subsection*{Articles in Preparation}
    \begin{etaremune}
        \item \underline{Verma, R.} \& Ukkusuri, S.V. Vehicular emission equity estimation using mobile phone geolocation data.
        
        \item \underline{Verma, R.}, Debnath, M., Mittal, S. \& Ukkusuri, S.V. Towards a generalized accessibility measure for transportation equity and efficiency. Economics ArXiv (2024). doi: \href{https://arxiv.org/abs/2404.04985}{arXiv:2404.04985}
    
        \item \underline{Verma, R.}, Ka, E. \& Ukkusuri, S.V. Long-term forecasts of statewide travel demand patterns using large-scale mobile phone GPS data: A case study of Indiana.
        % \\ Submitted to \textit{Transportation Research Record}.
    \end{etaremune}
\end{rSection}

% PUBLICATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Presentations}
    \begin{etaremune}
        \item \underline{Verma, R.} Assessing Indiana's transportation and environmental equity using large-scale data. \textit{ASCE International Conference on Transportation \& Development}, Atlanta (Jun 2024). Research poster.

        \item \underline{Verma, R.} \& Debnath, M. Transportation equity assessment in Indiana: Recent findings. \textit{110th Purdue Road School Conference and Expo}, West Lafayette, IN (Mar 2024). Oral presentation.
        
        \item \underline{Verma, R.}, Debnath, M., Mittal, S. \& Ukkusuri, S.V. Towards a generalized accessibility measure for transportation equity and efficiency. \textit{Joint Transportation Research Program Poster Session}, Indianapolis (Feb 2024). Research poster.
        
        \item \underline{Verma, R.} \& Ukkusuri, S.V. What determines distance decay? Understanding impedance decay in spatial interaction and accessibility. \textit{Joint Transportation Research Program Poster Session}, Indianapolis (Feb 2024). Research poster.

        \item \underline{Verma, R.}, Mittal, S., Lei, Z., Chen, X. \& Ukkusuri, S.V. Comparison of home detection algorithms using smartphone GPS data. \textit{Transportation Research Board 103rd Annual Meeting}, Washington D.C. (Jan 2024). Research poster.

        \item \underline{Verma, R.} \& Ukkusuri, S.V. Leveraging large-scale cell phone geolocation data to inform high-resolution transportation planning in Indiana. \textit{109th Purdue Road School Conference and Expo}, West Lafayette, IN (Mar 2023). Research poster.

        \item \underline{Verma, R.}, Deodhar, S., Ukkusuri, S.V. \& Gkritza, N. Measuring Indiana's transportation equity using large-scale data. \textit{109th Purdue Road School Conference and Expo}, West Lafayette, IN (Mar 2023). Research poster.

        \item \underline{Verma, R.} \& Ukkusuri, S.V. Crosswalk detection from satellite imagery for pedestrian network completion. \textit{Transportation Research Board 102nd Annual Meeting}, Washington D.C. (Jan 2023). Oral presentation.

        \item \underline{Verma, R.}, Shen, J., Murray-Tuite, P., Lee, S., Ge, Y. \& Ukkusuri, S.V. How hurricane evacuation dynamic decision-making progresses with information-seeking behavior. \textit{INFORMS: Mini-conference on `Decision Making for Emerging Risks'}, online (Jun 2021) (Oral presentation) and
        \\ \textit{Transportation Research Board 100th Annual Meeting}, Washington D.C. (Jan 2022) (Research poster).
    
        \item Paul, M., \underline{Verma, R.} \& Ghosh, I. An efficient calibration methodology of microsimulation model for signalized intersections under heterogeneous and indisciplined traffic environment. \textit{Transportation Research Board 98th Annual Meeting}, Washington D.C. (Jan 2019). Research poster.
        
        \item \underline{Verma, R.}, Saedi, R., Zockaie, A. \& Gates, T.J. Behavioral analysis of drivers following winter maintenance trucks enabled with collision avoidance system. \textit{Transportation Research Board 98th Annual Meeting}, Washington D.C. (Jan 2019). Oral presentation.

        \item Saedi, R., \underline{Verma, R.}, Zockaie, A. \& Ghamami, M. Large-scale emission estimation framework by incorporating the network-wide fundamental diagram: Introduction to network-wide emission diagram. \textit{International Conference on Transportation \& Health}, Mackinac Island, MI (Jun 2018). Research poster.
    \end{etaremune}
\end{rSection}

\begin{rSection}{Research Projects}
    \begin{etaremune}
        \item Ukkusuri, S.V., Gkritza, K., \underline{Verma, R.}, Rao, R., Debnath, M., Holguin, D. \& Deodhar, S. Addressing accessibility, equity, and environmental justice measures of infrastructure facilities in Indiana. \textit{Joint Transportation Research Program} project \# SPR 4711 (expected Oct 2024).
        
        \item RAPID/Collaborative research: Examining household movements and evacuation decision-making in a compounding risk event. \textit{National Science Foundation}, Award \#2153919 and \#2153913 (submitted Apr 2024).

        \item \underline{Verma, R.}, Luo, H., Deodhar, S., Ka, E., Chahine, R., Natu, P., Malhotra, H., Polisetty, V., Thakkar, D. J., Ukkusuri, S. V., Cai, H., Dunlop, S. R., Iyer, A. V., \& Gkritza, K. Forecasting shifts in Hoosiers' travel demand and behavior. \textit{Joint Transportation Research Program}, West Lafayette, Purdue University. Publication No. FHWA/IN/JTRP-2023/28 (Nov 2023). doi: \href{https://doi.org/10.5703/1288284317685}{10.5703/1288284317685}

        \item Ukkusuri, S.V., Murray-Tuite, P., Lee, S., Ge, Y., Lei, Z., \underline{Verma, R.}, Gehlot, H., Xue, J., Shen, J., Zhan, X., Qian, X., Le, T., et al. Hazards SEES: Bridging information, uncertainty, and decision-making in hurricanes using an interdisciplinary perspective. \textit{National Science Foundation}, Award \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1520338}{\#1520338} (Oct 2021).
        
        \item Zockaie, A., Saedi, R., Gates, T.J., Savolainen, P.T., Schneider, B., Ghamami, M., \underline{Verma, R.}, Fakhrmoosavi, F., Kavianipour, M., Shojaie, M., Singh, H., Zhou, C. Evaluation of a collision avoidance and mitigation system (CAMS) on winter maintenance trucks. \textit{Michigan Department of Transportation Research Administration}, \href{https://rosap.ntl.bts.gov/view/dot/42752}{OR 17-103} (Sep 2018).
    \end{etaremune}

\end{rSection}

% AWARDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Awards \& Honors}%
    \textbf{Outstanding Service in Graduate Education} \hfill {4/2024}
    \\ College of Engineering, Purdue University (\$2,000) \\
    % Yoder Award
    \\ \textbf{Eldon J. Yoder Memorial Award} \hfill {9/2023}
    \\ Transportation Area Grad Awards, Lyles School of Civil Engineering, Purdue University (\$750) \\
    % Best ITE Student Chapter
    \\ \textbf{Best ITE Student Chapter Award} \hfill {8/2023}
    \\ (Received as outgoing chapter president)
    \\ Great Lakes ITE District Annual Meeting, Grand Rapids, MI (\$500)
    \\ ITE International and West District Annual Meeting, Portland, OR (\$1,000) \\
    % WSP article on crosswalk detection
    % \\ \textbf{\href{https://www.washingtonpost.com/transportation/2023/02/25/sidewalks-crosswalks-study/}{News article} by \textit{The Washington Post}} \hfill {2/2023}
    % \\ (For the paper \textit{Crosswalk detection from satellite imagery for pedestrian network completion}) \\
    % Flannigan travel award
    \\ \textbf{Erin Flannigan Travel Award} \hfill {11/2022}
    \\ 102nd Transportation Research Board Annual Meeting (\$300) \\
    % Best MS student
    \\ \textbf{M.S. Student of the Year} \hfill {5/2019}
    \\ Department of Civil Engineering, Michigan State University \\
    % ITE scholarship
    \\ \textbf{Annual ITE Scholarship} \hfill {2/2019}
    \\ Institute of Transportation Engineers - Michigan Chapter (\$3,000) \\
    % Student travel for ICTH
    \\ \textbf{Student Travel Award} \hfill {6/2018}
    \\ 2018 International Conference on Transport \& Health (\$800) \\
    % Best poster
    \\ \textbf{Best Poster in Civil Engineering (Transportation)} \hfill{3/2018}
    \\ 2018 Engineering Graduate Research Symposium, Michigan State University \\
    % MCM
    \\ \textbf{Merit-cum-Means Scholarship} \hfill{1/2014 - 4/2015}
    \\ Indian Institute of Technology Roorkee, INR 200,000 ($\approx$\$2,600) over 2 years
\end{rSection}

% COURSES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Extracurricular Coursework}
    \textbf{Teaching and Learning in Engineering Graduate Certificate} \hfill{5/2023}
    \\ Certificate program at Purdue University's School of Engineering Education (ENE), including:
    \begin{itemize}
        \item ENE 506: Content, Assessment, and Pedagogy
        \item ENE 685: Engineering Education Methods
        \item ENE 687: Mentored Teaching in Engineering
        \item ENE 695: Succeeding as an Engineering Professor
    \end{itemize}
    % Intro to Tensorflow
    \textbf{Complete Guide to Tensorflow for Deep Learning with Python} \hfill 5/2021
    \\ (\href{https://www.udemy.com/certificate/UC-caa1f4ed-6be6-4b50-9bd1-1b57ab7c196a}{Udemy}) \\
    % Text mining
    \\ \textbf{Text Mining and Analytics} \hfill 2/2020
    \\ University of Illinois, Urbana-Champaign (\href{https://coursera.org/share/7eac25e880771bf576b661324a4d79be}{Coursera}) \\
    % Intro to graph theory
    \\ \textbf{Introduction to Graph Theory} \hfill 7/2018
    \\ University of California, San Diego (\href{https://coursera.org/share/97583460aa0510f570f971844f19d16b}{Coursera}) \\
    % Bayesian stats
    \\ \textbf{Bayesian Statistics} \hfill 5/2018
    \\ University of California, Santa Cruz (\href{https://coursera.org/share/8d0b0387400c53f13a7ce2b2b81153fc}{Coursera}) 
\end{rSection}

% -------------------------
% STUDENT ORGANIZATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%
% -------------------------
\begin{rSection}{Memberships and Service}
    % -------------------------
    % Professional
    % -------------------------
    \subsection*{Professional Organizations}
    \begin{itemize}
        \item American Society of Civil Engineers \hfill 3/2018 – 3/2019
        \\ (Student member)
        \item Institute of Transportation Engineers \hfill 12/2017 – Present \\
        (Served in Purdue Chapter as president (2022–23), vice-president (2021–22) \& treasurer (2020–21))
    \end{itemize}
    % -------------------------
    % Student clubs
    % -------------------------
    \subsection*{Student Bodies}
    \begin{itemize}
        \item Purdue Graduate Student Government, \textit{Purdue University} \hfill 3/2020 – 4/2021
        \item Civil Engineering Graduate Student Advisory Council, \textit{Purdue University} \hfill 9/2019 – Present \\
        (Served as vice-president during 2020–21)
        \item Graduate Employees Union, \textit{Michigan State University} \hfill 11/2018 – 5/2019 \\
        (Chair of the \emph{Deferred Actions for Childhood Arrivals} (DACA) Committee)
        \item Civil Engineering Consortium, \textit{I.I.T. Roorkee} \hfill 7/2016 – 12/2016
        \\ (Graphic design lead)
        \item Information Management Group, \textit{I.I.T. Roorkee} \hfill 2/2015 – 5/2017
        \\ (Design and Creativity Head)
    \end{itemize}
    % -------------------------
    % Volunteer service
    % -------------------------
    \subsection*{Volunteer Service}
    \begin{itemize}
        \item Purdue's Algebra by 7th Grade \hfill 1/2023
        \\ (Assisted high-performing students of color of 7th grade with math and English)
        \item Briarwood \& RichField Tutoring \& Life Skills Program \hfill 9/2021 – 12/2021
        \\ (Tutored and assisted in homework kids of color in grades 1–4)
        \item National Service Scheme, \textit{I.I.T. Roorkee} \hfill 8/2013 – 7/2014
        \\ (Conducted several awareness activities as part of the \textit{Environment} section)
    \end{itemize}

\end{rSection}

\vspace*{\fill}
\centering Updated April 20, 2024

\end{document}
